
---
title: "Report"
author: "Hyoungchul Kim"
date: "`r Sys.Date()`"
output:
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 2
format: 
  pdf:
    keep-tex: true
    include-in-header: 
       text: |
         \usepackage{fvextra}
         \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
         \DefineVerbatimEnvironment{OutputCode}{Verbatim}{breaklines,commandchars=\\\{\}}
---

## 1.

We will use the fact that in optimal policy, $\frac{\partial \mathcal{L}}{\partial t} = 0$.

\begin{align}
  0 &= \frac{\partial \mathcal{L}}{\partial t}\\
    &= - \int_i G' \left( U'_{ic} \left( \frac{\partial z_i}{\partial t} - z_i - t \frac{\partial z_i}{\partial t}\right) + U'_{iz} \frac{\partial z_i}{\partial t} \right)dv(i) + \lambda \int_i \left( z_i + t \frac{\partial z_i}{\partial t} \right)dv(i)\\
    &= - \int_i z_i U'_{ic} G' dv(i) + \lambda \int_i \left( z_i + t \frac{\partial z_i}{\partial t} \right)dv(i)
\end{align}

Rearranging and using $g_i$ and $\varepsilon_i$, we get:

$$
\int_i g_i z_i dv(i) = \int_i \left( z_i - \varepsilon_i \frac{t}{1-t} z_i \right)dv(i).
$$

After using the fact that $\varepsilon_i = \varepsilon^c_i = \eta_i$ and $g_i + \frac{t}{1-t} \eta_i = \tilde{g}_i$, we can simplify the equation to:

$$
  \int_i \tilde{g}_i z_i dv(i) = \int_i \left( z_i - \varepsilon^c_i \frac{t}{1-t} z_i \right)dv(i) \Rightarrow - \int_i \varepsilon^c_i \frac{t}{1-t}z_i dv(i) = \int_i \tilde{g}_i z_i - z_i dv(i).
$$

Since expectation of $\tilde{g}_i$ is 1, we can denote the right hand side of the equation as $\text{Cov} (\tilde{g}_i, z_i)$. Then assuming elasticity is same for everyone, we can get the equation in the question 7.

# Part 2: Numerical application

```{r}
#| echo: true
#| warning: false 
 
# Load libraries
library(tidyverse)
library(gt)

# Given parameters
t <- 0.3  # Current tax rate
b <- 5000 # Lump-sum benefit

```

```{r}
#| echo: true
#| message: false
#| warning: false 

implied_ability <- map(c(20000, 50000, 200000), ~ (.x / (1-t)^0.3)^(1/1.3)) |>
  bind_cols() |>
  rename_with(~ c("low", "middle", "high")) |> print() 
```
